---
title: "615 shiny"
author: "Yibing Wang"
output: html_document
date: "2024-11-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(shiny)
```

#Hadley_1

```{r}
ui <- fluidPage(
  selectInput("dataset", label = "Dataset", choices = ls("package:datasets")),
  verbatimTextOutput("summary"),
  tableOutput("table")
)


server <- function(input, output, session) {
  output$summary <- renderPrint({
    dataset <- get(input$dataset, "package:datasets")
    summary(dataset)
  })
  
  output$table <- renderTable({
    dataset <- get(input$dataset, "package:datasets")
    dataset
  })
}

shinyApp(ui, server)
```

#Hadley_2

```{r}
ui <- fluidPage(
  selectInput("dataset", label = "Dataset", choices = ls("package:datasets")),
  verbatimTextOutput("summary"),
  tableOutput("table")
)

server <- function(input, output, session) {
  # Create a reactive expression
  dataset <- reactive({
    get(input$dataset, "package:datasets")
  })

  output$summary <- renderPrint({
    # Use a reactive expression by calling it like a function
    summary(dataset())
  })
  
  output$table <- renderTable({
    dataset()
  })
}
shinyApp(ui, server)
```

Hadley_1 fetches the dataset multiple times.
Hadley_2 fetches the dataset once and reuses it, making it more efficient.

# 2.3.5
1.
a. renderPrint(summary(mtcars)) <- verbatimTextOutput()

b. renderText("Good morning!") <- textOutput()

c. renderPrint(t.test(1:5, 2:6)) <- verbatimTextOutput()

d. renderText(str(lm(mpg ~ wt, data = mtcars))) <- textOutput()

2.
```{r}

ui <- fluidPage(
  plotOutput("plot", height = "300px", width = "700px")
)
server <- function(input, output, session) {
  output$plot <- renderPlot(plot(1:5), res = 96)
  output$plot_description <- renderText({
    "Scatterplot of Random Numbers"
  })
}
shinyApp(ui, server)

```

3.
```{r}
ui <- fluidPage(
  dataTableOutput("table")
)

server <- function(input, output, session) {
  output$table <- renderDataTable(mtcars, options = list(pageLength = 5))
}
shinyApp(ui, server)
```

4.
```{r}
library(reactable)

ui <- fluidPage(
  reactableOutput("table")
)

server <- function(input, output) {
  output$table <- renderReactable({
    reactable(mtcars)
  })
}

shinyApp(ui, server)
```

# 3.3.6
1.
```{r}
ui <- fluidPage(
  textInput("name", "What's your name?"),
  textOutput("greeting")
)

server1 <- function(input, output, session) {
  output$greeting <- renderText({
    paste0("Hello ", input$name)
  })
}

server2 <- function(input, output, session) {
  output$greeting <- renderText({
    paste0("Hello ", input$name)
  })
}

server3 <- function(input, output, session) {
  output$greeting <- renderText({
    paste0("Hello ", input$name)
  })
}

shinyApp(ui, server)
```

2.
Server 1 Reactive Graph:

input$a ---->
             \
               -> c() --> e() --> output$f
             /
input$b ---->             ^
                          |
                      input$d
                    
Server 2 Reaction Graph:

input$x1 ----> 
               \
input$x2 ----> --> x()  --> \
               /
input$x3 ---->                \
                                --> output$z
input$y1 ---->
              \               /
                ->  y() ----/
              /
input$y2 ----> 

Server 3 Reactive Graph:

input$a ----> a() ----> b() ----> c() ----> d()
                   ^         ^         ^
                   |         |         |
                 input$b     |         |
                          input$c      |
                                    input$d
                                    
3.
fail because of name conflict.
range and var are  R functions, so we cannot set range as a veriable name. we can rename the code.
```{r}
variable <- reactive(df[[input$var]])
variable_range <- reactive(range(var(), na.rm = TRUE))
```

# 4.8
1.
4.8
1.

                    
                     input$code 
                           │
                           ▼
                      selected()          
            (filters injuries based on prod_code)
                     │                   |
                     │                   |
                     ▼                   ▼
                output$diag         output$body_part
          (table count by diag)  (table count by body_part)  
                      │
                      │
                      ▼
                output$location   
            (table count by location)     
                      ▲
                      |
                      │
                   summary()             
      (count by age, sex, then joined with population)      
      
                        │
                        |
                        ▼
                  output$age_sex        
        (line plot by age, n per age-sex group) 




                      input$code 
                           │
                           ▼
                      selected()          
            (filters injuries based on prod_code)
                     │                   |
                     │                   |
                     ▼                   ▼
                output$diag         output$body_part
          (table count by diag)  (table count by body_part)  
                      │
                      │
                      ▼
                output$location   
            (table count by location)     
                      ▲
                      |
                      │
                   summary()             
      (count by age, sex, then joined with population)      
                        |
                        │
                        ▼
                     input$y                                 
           (user choice: rate vs count)     
                        │
                        |
                        ▼
                  output$age_sex        
        (line plot by age, rate or count based on input$y) 





                      input$code 
                           │
                           ▼
                      selected()          
            (filters injuries based on prod_code)
                     │                   |
                     │                   |
                     ▼                   ▼
                output$diag         output$body_part
          (table count by diag)  (table count by body_part)  
                      │
                      │
                      ▼
                output$location   
            (table count by location)     
                      ▲
                      |
                      │
                   summary()             
      (count by age, sex, then joined with population)
                        |
                        │
                        ▼
                  output$age_sex                                  
       (conditional plot by age: rate or count) 
                        |
                        │
                        ▼
                   input$story          
                        |
                        │
                        ▼
                narrative_sample()    
          (gets new narrative on button click)       
                        |
                        │
                        ▼
                output$narrative       
          (displays current narrative text)       

2.
Using fct_infreq() after fct_lump() will order the levels by frequency after lumping the rare levels together.
Using fct_lump() after fct_infreq() will first order the levels by frequency, but the lumping might not align with the frequencies anymore because the original dataset isn't grouped by frequency.

3.
```{r}
#column(4, sliderInput("num_rows", "Number of rows:", min = 1, max = 10, value = 5)

#output$diag <- renderTable({count_top(selected(), diag, n = input$num_rows)}, width = "100%")
#output$body_part <- renderTable({count_top(selected(), body_part, n = input$num_rows)},width="100%")
#output$location <- renderTable({count_top(selected(), location, n = input$num_rows)}, width ="100%")
```

4.
```{r}
#fluidRow(
    #column(2, actionButton("prev", "Previous")),
    #column(2, actionButton("next", "Next")),
    #column(8, textOutput("narrative"))
```




